Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-14 WRITEUP/table_medianLens.tex
in response to referee

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Lens parameters constrained by models of seven velocity channels}
\tablehead{
\multicolumn{2}{c}{Parameters} &
\colhead{Median values} % weighted-mean of median of each
}
\startdata
Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
Axial Ratio      &             & 0.56$\pm$0.16\\
Position Angle   & (deg)       & 103$\pm$22\\
Einstein Radius  & (\arcsec)   & 1.833$\pm$0.002
\enddata
\label{tab:lens}
\tablecomments{Parameters describing the foreground lens are
obtained based on the median in the preliminary models (see text for details).
All angular offsets are with respect to
$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
$\delta$\,=\,$-$12\degr31\arcmin58\farcs3 (J2000).}
\end{deluxetable}

>>>>

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Lens parameters constrained by models of seven velocity channels}
\tablehead{
\multicolumn{2}{c}{Parameters} &
\colhead{Median values} % weighted-mean of median of each
}
\startdata
Offset in RA    & (\arcsec)   &  0.004$\pm$0.027\\
Offset in Dec    & (\arcsec)   & 0.003$\pm$0.027\\
Axial Ratio      &             & 0.56$\pm$0.16\\
Position Angle   & (deg)       & 103$\pm$22\\
Einstein Radius\tna  & (\arcsec)   & 1.833$\pm$0.002
\enddata
\label{tab:lens}
\tablenotetext{a}{This corresponds to mass of $M(\theta$\,$<$\,$\theta_{\rm E})$\eq(7.42\pmm0.02)\E{11}\Msun within the Einstein radius.}
\tablecomments{Parameters describing the foreground lens are
obtained based on the median in the preliminary models (see text for details).
All angular offsets are with respect to
$\alpha$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44,
$\delta$\,=\,$-$12\degr31\arcmin58\farcs3 (J2000).}
\end{deluxetable}
